---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# impute


NOTE : This package is still in the early stage of development! 

This is an R package that wrapps the most popular algorithms for data imputation. Its objective is to allow the evaluation of these methods in terms of bias (robustness) and prediction (accuracy). 

# Install instruction

```{r, eval=FALSE}
#devtools::install_github("ielbadisy/impute")
# generate_na

irisNA <- impute::generate_na(iris)
irisNAx <- impute::impute(irisNA, "knn") # impute(<incomplete_dataset>, "<imputation_method>")
```

Currently, only the methods bellow are implemented :

   * `naive`: mean/mode   
   * `hotdeck`
   * `knn` 
   * `cart`
   * `glmnet`
   * `missranger`
   * `missforest`
   * `spmm`
   * `famd`
   * `mpmm`
   * `micerf`
   * `supermice`
